Notes on two photon scattering of the molecular state

### 2019-11-24 notes/two-photon-broadening/note.tex
[notes/two-photon-broadening] Finish two photon coupling up

\subsubsection{Single photon off resonance scattering from coupled excited state}
\begin{wrapfigure}{R}{10cm}
  \begin{center}
    \begin{tikzpicture}
      \draw[->, line width=2] (0, -0.5) -- (0, 3.5);

@@

      \begin{scope}[shift={(3, 0)}]
        % \draw[dashed] (-0.05, 0) -- (1.5, 0);
        % \draw[dashed] (-0.05, 2.15) -- (1.5, 2.15);
        % \draw[dashed] (-0.05, 2.45) -- (1.5, 2.45);

@@

>>>>

\subsubsection{Single photon off resonance scattering from coupled excited state}
\begin{wrapfigure}{R}{7.3cm}
  \begin{center}
    \begin{tikzpicture}
      \draw[->, line width=2] (0, -0.5) -- (0, 3.5);

@@

      \begin{scope}[shift={(2.6, 0)}]
        % \draw[dashed] (-0.05, 0) -- (1.5, 0);
        % \draw[dashed] (-0.05, 2.15) -- (1.5, 2.15);
        % \draw[dashed] (-0.05, 2.45) -- (1.5, 2.45);

@@

The correct way to calculate this requires using the dipole moment between the states
\footnote{And the formula also correctly takes into account the density of state of
  the scattered photon and gives the correct
  $\paren{\dfrac{2\omega}{\omega+\omega_0}}^3$ factor}.
For the purpose of this note, however, it is enough to only calculate the interference term
and scales our previous result correspondingly.\\

Let the $D_1=\langle g|\hat d|e_1\rangle$ and $D_2=\langle g'|\hat d|e_2\rangle$ be
the dipole moment coupling $e_1$ and $e_2$ to the corresponding ground states $g$ and $g'$.
The dipole moments between the new states are shown in figure \ref{two-up-coupled}B
\footnote{The sign of the dipole moment depends on the selection of the phase for
  $|\pm\rangle$ but the relative sign of the product does not depend on the phase selection}.\\

The wrong way to calculate the scattering gives a factor of
\eqar{
  &\paren{\frac{D'}{\sqrt2}\frac{D_1}{\sqrt2}\frac{1}{\Delta+\Omega_2/2}}^2+\paren{\frac{-D'}{\sqrt2}\frac{D_1}{\sqrt2}\frac{1}{\Delta-\Omega_2/2}}^2\\
  \approx&2\paren{\frac{D'}{\sqrt2}\frac{D_1}{\sqrt2}\frac{1}{\Delta}}^2\\
  =&\frac{D'^2D_1^2}{2\Delta^2}
}
The correct way gives,
\eqar{
  &\paren{\frac{D'}{\sqrt2}\frac{D_1}{\sqrt2}\frac{1}{\Delta+\Omega_2/2}+\frac{-D'}{\sqrt2}\frac{D_1}{\sqrt2}\frac{1}{\Delta-\Omega_2/2}}^2\\
  =&\frac{D'^2D_1^2}{4}\paren{\frac{1}{\Delta+\Omega_2/2}-\frac{1}{\Delta-\Omega_2/2}}^2\\
  =&\frac{D'^2D_1^2}{4}\paren{\frac{\Delta-\Omega_2/2-\Delta-\Omega_2/2}{\Delta^2-\Omega_2^2/4}}^2\\
  \approx&\frac{D'^2D_1^2\Omega_2^2}{4\Delta^4}
}
which means that we should scale the incorrect result above by
\[\frac{D'^2D_1^2\Omega_2^2}{4\Delta^4}\frac{2\Delta^2}{D'^2D_1^2}=\frac{\Omega_2^2}{2\Delta^2}\]
and the correct answer is
\eqar{
  \gamma=&\frac{\Gamma}{8}\frac{\Omega_1^2}{\Delta^2}\frac{\Omega_2^2}{2\Delta^2}\\
  =&\frac{\Gamma}{16}\frac{\Omega_1^2\Omega_2^2}{\Delta^4}
}
which is exactly what we got above.
